---
title: "Quarto with wide DT datatable objects in widened container: DT page controls do not work properly"
number-sections: true
format: 
  html: default
---

## Issue

When displaying wide DT::datatable in Rstudio with quarto, and the table is **too wide** for the page:

-   IF an html div widens the container,

-   THEN the clickable page controls below the table, i.e.,

> Previous, 1, 2, 3, 4, 5, ..., 10 Next

-   do NOT work properly. For example, 1 and 10 may respond to clicks, but 2-5 may not. Or, if you click 10, making 6-9 visible, 9 will respond to a click, but 6-8 will not.

-   This behavior occurs if the html is rendered and viewed in a web browser (Chrome).

-   However, if the html is rendered and viewed in the viewer pane, the page controls work properly.

-   If this qmd file is converted to an rmd markdown file and knit as rmd (without quarto), this behavior does not occur - page controls work properly. In addition, the page automatically is much wider than the page rendered in quarto.


## Environment

-   Windows 10 x64 (build 22598)
-   R version 4.1.3 (2022-03-10)
-   RStudio-2022.06.0-daily-322.exe
-   quarto-0.9.299-win.msi
-   DT 0.22 2022-03-28


## Make data frame that will be too wide for page

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(DT)
# devtools::session_info()
# devtools::package_info()
# quarto render gt_quarto_mre.qmd

# make a wide data frame
nvars <- 30
ncols <- nvars + 1
nrows <- 100
(colnames <- c("id", paste0("x", 1:nvars)))

df <- matrix(data=1:(ncols * nrows), 
             nrow=nrows, 
             dimnames=list(NULL, colnames)) %>%
  as_tibble()

```

## Show DT object without changing page width

-   page display controls work properly

```{r}

datatable(df)

```

## Show DT object with a div that has no options

-   page display controls work properly

::: {style=""}
<!-- <div style = "width: 1200px; height:auto; margin: auto; font-size: 8pt;"> -->

```{r}

datatable(df)

```
:::

## Show DT object with div style = "width: 1200px;"

-   this div is wider than the page
-   clickable page display controls no longer work properly
-   (Note that quarto converted `<div style = "width: 1200px;">` to `::: {style="width: 1200px;"}`)

::: {style="width: 1200px;"}
<!-- <div style = "width: 1200px;"> --> 
```{r}

datatable(df)

```
:::


## Sessioninfo

```{r}
sessionInfo()
```



