# Create data

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(gt)

df <- tibble(rank=1:10, money=seq(100, 1000, 100))

```

# This renders in html and pdf format

Note that, in html format and in pdf format:

-   labels work for plain text, whether designated as html or not, and

-   labels work for text with a \$ sign, when not designated as html.

```{r}
df %>% 
  gt() %>% 
  cols_label(rank=html("Rank"), money="Amount $")
```

# This renders as html but generates error as pdf

Here "Amount \$" is enclosed in html(). The error is:

> You may need to \$ \$ around an expression in this file.

```{r}
#| eval: false

# set eval to false to continue on to next chunk and render as pdf without error
df %>% 
  gt() %>% 
  cols_label(rank=html("Rank"), money=html("Amount $"))

```


# Escaping the $ allows this to render as pdf but a slash shows in html output
```{r}

df %>% 
  gt() %>% 
  cols_label(rank=html("Rank"), money=html("Amount<br>\\$"))

```


# Using md allows this to render as pdf but it renders differently in html and pdf
```{r}

df %>% 
  gt() %>% 
  cols_label(rank=html("Rank"), money=md("Amount<br>$"))

```



